A community-maintained standard library of population genetic models

### 2019-12-22 popSimManu.tex

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/n_t_dag.pdf}
\caption{\textbf{Workflow for our N(t) inference methods comparison.}
Here we show single replicate for two chromosomes, chr22 and chrX, simulated under the HomSap 
OutOfAfrica\_3G09 demographic model, with a HapmapII\_GRCh37 genetic map.
Note that resulting data for input to all inference methods \smcpp, \MSMC, and \stairwayplot,
come from the same set of simulations.}
\label{fig:n_t_dag}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/two_pop_dag.pdf}
\caption{\textbf{Workflow for our two population N(t) inference methods comparison}
Here we show single replicate for one chromosome, chr22, simulated under the HomSap 
OutOfAfrica\_3G09 demographic model, with a HapmapII\_GRCh37 recombination map.
Note that resulting data for input to all inference methods \dadi, \smcpp,
and \fastsimcoal,
derive from the same set of simulations.}
\label{fig:two_pop_dag}
\end{center}
\end{figure}
